### 2014-02-28 paper/concrete.tex
checkpoint.

@@

\begin{theorem}[Weak isomorphism preserves termination insensitive non-interference]
  If a language \con{L} is weakly isomorphic to a language \abs{L}, and \abs{L}
  satisfies TINI, then \con{L} satisfies TINI.
\end{theorem}

@@

A na\"ive attempt at our single heap semantics
will not allow us to construct an isomorphism
with the abstract language |specLangML alpha|, and instead highlights
where things will go wrong.
To successfully construct an isomorphism, our concrete semantics need
to mirror the behavior of the abstract semantics, most importantly
in the case where tasks interact.  Namely, at a fork and when sending
or receiving messages, we take an expression from one task and
execute it in the context of another task.  In the abstract semantics
the fork rule

>>>>

\begin{theorem}[Isomorphism preserves termination sensitive non-interference]
  \label{thm:iso-tsni}
  If \ifc{L} is isomorphic to \tar{L} and \ifc{L} satisfies TSNI, then
  \tar{L} satisfies TSNI.
\end{theorem}

@@

\begin{theorem}[Weak isomorphism preserves termination insensitive non-interference]
  \label{thm:iso-tini}
  If a language \con{L} is weakly isomorphic to a language \abs{L}, and \abs{L}
  satisfies TINI, then \con{L} satisfies TINI.
\end{theorem}

@@

A na\"ive attempt at our single heap semantics
will not allow us to construct an isomorphism
with the abstract language |specLangML alpha|, and instead highlights
where things will go wrong.
To successfully construct an isomorphism, our concrete semantics need
to mirror the behavior of the abstract semantics, most importantly
in the case where tasks interact.  Namely, at a fork and when sending
or receiving messages, we take an expression from one task and
execute it in the context of another task.  In the abstract semantics
the fork rule is parameterized by the strategy |klone| which defines
what heap the new task should execute in.  \Red{In Section~\ref{sec:retrofit}
we have motivated two choices}, namely the identity (to effectively
clone the heap), or to start with an empty heap.
In the latter case, this effectively means that existing addresses
in the forked expression |ie| are no longer valid and the
task gets stuck (and then removed by \textsc{I-noStep}).
\todo{}{Is this actually true?  Currently the semantics are unclear.}
To get the isomorphic behavior in the concrete semantics with a
single heap, we would have to change the forked expression |ie| in
such a way that all addresses get rewritten to fresh addresses
that are guaranteed to not occur in the global heap.  Similarly,
sending a memory address should take a similar approach, as addresses
for sent references will not exist in the receiving task.

If |klone| is the identity function, then the abstract semantics
effectively clone the heap on a fork.  To get an isomorphic
behavior in the concrete, we would have to create a copy of everything
reachable from the forked expression (not just the values for
the memory addresses in the expression), and replace all addresses
correspondingly.  Even worse, the behavior of sending a memory address
now depends on whether that address existed at the time the receiving
task was forked;  if it did, then the address should be rewritten to the
new one, otherwise to a fresh address.
Such a complicated behavior is contradictory to our initial motivation
of implementing a single heap for efficiency.  But also the
behavior of the simpler case where |klone| returns an empty heap is
undesirable:  We rewrite addresses to fresh addresses, which will
result in a stuck task whenever such an address is dereferenced.

\subsection{Restricting the IFC Language}

As a better solution we could forbid forked expressions as well
as messages sent to other tasks to contain memory addresses in the
first place.  In a statically typed language, the type system could
prevent this from happening, and we talk more about how our
approach integrates with typed languages in
Section~\ref{sec:extensions:types}.
In a dynamically type languages such as |targetLangML|, we might
restrict the transition for |fork| and |send| to only allow expressions
without memory addresses.

Again we are modifying the IFC language semantics in a non-trivial way,
which begs the question whether non-interference is preserved.
Note that restricting the transitions in an information flow control
system in general is not non-interference preserving as the following
minimal example illustrates.
Consider a trivial state machine as shown
in Figure~\ref{fig:trivial-sm}, whose second projection is classified
secret.  With all three transitions, this language fulfills
termination sensitive non-interference.  Furthermore, if the
dashed transition
is removed, the language continues to satisfy TSNI.  However, if any
solid line is removed, the language fails TSNI.

To remedy this issue, we give a definition that gives a condition
under which it is safe to restrict the abstract IFC language
|specLang alpha targetLang|, such that non-interference is preserved.

\begin{definition}[Restricted IFC language]
  \label{def:npri}
  For a family of predicates $\mathcal P$ (one for every reduction
  rule), we call
  |restrictedLang alpha targetLang| a restricted IFC language
  if its definition is equivalent to the abstract language
  |specLang alpha targetLang|, with the following exception:
  The reduction rules are restricted
  by adding a predicate $P$ from $\mathcal P$ to the premise of
  any rule other than \textsc{I-noStep}.  Furthermore, the predicate $P$
  can depend only on the \textit{erased} configuration
  |erase il ic|, where |il| is the label of the first task
  in the task list and |ic| the full configuration.
\end{definition}

By the following theorem, the restricted IFC language with an
appropriate scheduling policy is non-interfering.

\begin{theorem}
  \label{thm:restricted}
  For any target language |targetLang| and family of predicates
  $\mathcal{P}$, the IFC language |restrictedLang roundrobinf targetLang|
  is TSNI.  Furthermore, the IFC language
  |restrictedLang seqf targetLang| is TSNI.
\end{theorem}

\subsection{IFC language with a single heap}

We are now ready to make our single heap IFC language precise and
ensure its non-interference using the techniques presented.
First, we can construct the restricted language
|restrictedLangNoRef alpha targetLangML|, where |noRefs| is
the family of always valid predicates, except for the ones for
\textsc{I-fork} and \textsc{I-send}, which we define as
\[ P = \text{|ie| does not contain any address |ta|} \]
Since $P$ only depends on |ie|, which is part of the current
task and thus never erased w.r.t.\ the label of the first task,
this language satisfies non-interference by Theorem~\ref{thm:restricted}.

The essential parts of the semantics for the concrete language
with a single heap are given in Figure~\Red{X}.  Most rules are
straight-forward translations of the rules in Figures~\ref{fig:ifc}
and~\ref{fig:embedding} but for a single heap.  For conciseness, we
only show the interesting ones.
Now, we can show an isomorphism between this language and
|restrictedLangNoRef alpha targetLangML|, which
(by Theorem~\ref{thm:iso-tsni} and~\ref{thm:iso-tini}) guarantees
non-interference for an appropriate scheduling policy |alpha|.

\Red{Show the isomorphism.}

\subsection{Old Stuff}
